\plaintitle

### 2016-09-21 drafts/labor/complexity.tex

\subsection[What are the complexity limits of crowd work]{Identifying the Complexity Limits of Crowd Work}\label{sec:complexity}

>>>>

\subsection[What are the complexity limits of crowd work]{Identifying the Complexity Limits of Crowd Work}\label{sec:complexity}
A key question to the future of on--demand work is \textit{what} precisely will become part of this economy. Paid crowdsourcing began with simple microtasks on platforms such as Amazon Mechanical Turk, but microtasks are only helpful if they build up to a larger whole. So, our first question: how complex can the work outcomes from crowd work be?

### 2016-09-21 drafts/labor/relationships.tex

\subsubsection{\pieceworkpers}
\topic{Despite the intense growth of the piecework approach to renumeration,
this time was not without turmoil.}
As previously discussed, a number of worker organizations weighed in on
(or, more precisely, against) piecework and the myriad oversights it made in valuing workers' time
\cite{american1921problem,richards1904anything}.
As mounting attention increasingly revealed problems in piecework as it related to workers,
workers themselves began to speak out about their frustration with this new regime.
\citeauthor{riisOtherSideLives}'s photo--documentary work
brought light to otherwise--invisible pieceworkers in their homes;
this and other events led to organizations representing
railway workers, mechanical engineers, and others
who began to mount advocacy in defense and favor of workers
\cite{american1921problem,richards1904anything,riisOtherSideLives}.
\citeauthor{10.2307/3827491} tells us of the match--girls strike of 1888,
one of the earliest and most famous successful worker strikes and perhaps
the beginning of ``militant trade unionism''
\cite{10.2307/3827491}.
It wasn't an exaggeration when \citeauthor{weyer1894history} later said that
``the match--girls' victory turned a new leaf in Trade Union annals'' \cite{weyer1894history};
in the 30 years since the match--girls strike,
the Trade Union Movement grew from
``20 per cent of adult male manual--working wage--earners [to] over 60 per cent''
\cite{webb1920history}.

>>>>

\subsubsection{\pieceworkpers}
\citeauthor{clark1908cotton}, for instance,
relays his observations of textile mill pieceworkers and his realization that
``When he works by the day the Italian operative wishes to leave before the whistle blows,
but if he works by the piece he will work as many hours as it is possible for him to stand''

\citeauthor{riisOtherSideLives} was documenting abhorrent working \& living conditions of pieceworkers in New York City,
and \citeauthor{norton1900textile} was providing substantive guidance on various wage regimes,
offering guidance on how best to manage pieceworkers
\cite{riisOtherSideLives,norton1900textile}.

\topic{Despite the intense growth of the piecework approach to renumeration,
this time was not without turmoil.}
As previously discussed, a number of worker organizations weighed in on
(or, more precisely, against) piecework and the myriad oversights it made in valuing workers' time
\cite{american1921problem,richards1904anything}.
As mounting attention increasingly revealed problems in piecework as it related to workers,
workers themselves began to speak out about their frustration with this new regime.
\citeauthor{riisOtherSideLives}'s photo--documentary work
brought light to otherwise--invisible pieceworkers in their homes;
this and other events led to organizations representing
railway workers, mechanical engineers, and others
who began to mount advocacy in defense and favor of workers
\cite{american1921problem,richards1904anything,riisOtherSideLives}.
\citeauthor{10.2307/3827491} tells us of the match--girls strike of 1888,
one of the earliest and most famous successful worker strikes and perhaps
the beginning of ``militant trade unionism''
\cite{10.2307/3827491}.
It wasn't an exaggeration when \citeauthor{weyer1894history} later said that
``the match--girls' victory turned a new leaf in Trade Union annals'' \cite{weyer1894history};
in the 30 years since the match--girls strike,
the Trade Union Movement grew from
``20 per cent of adult male manual--working wage--earners [to] over 60 per cent''
\cite{webb1920history}.
